\section{Overview of the Biological Risk-Analysis Model}

The framework was designed as a post-processing risk-analysis layer applied to a fixed physical lattice dose distribution rather than as a treatment optimizer. For each case, a voxelized absorbed-dose grid $D_{\mathrm{phys}}(\mathbf{x})$ was first generated with Monte Carlo transport. This physical dose was then evaluated in three modes: physical only, biology-informed without vascular uptake, and biology-informed with anatomy-aware vascular uptake. The purpose of this comparison was to test whether cases that appeared similar under physical dose metrics remained similar after non-local biological burden was taken into account.

The biology-informed modes treated irradiation as a source of diffusible stress signals, including reactive oxygen species-like and cytokine-like species, that could spread beyond directly irradiated peaks into valley and peri-tumour regions. At a high level, each species concentration $c_k(\mathbf{x},t)$ evolved according to a reaction-diffusion equation of the form
\begin{equation}
\frac{\partial c_k}{\partial t}
= D_k \nabla^2 c_k - \lambda_k c_k - u_k(\mathbf{x}) c_k + S_k(\mathbf{x}),
\end{equation}
where $D_k$ is the diffusion coefficient, $\lambda_k$ is the decay term, $S_k(\mathbf{x})$ is the radiation-driven source term, and $u_k(\mathbf{x})$ is an optional uptake field. In the no-sink mode, $u_k(\mathbf{x})=0$. In the anatomical-sink mode, $u_k(\mathbf{x})$ was non-zero within artery and vein masks, so that vessels acted as spatially localized uptake regions for diffusible signalling.

The biological burden generated by the species fields was accumulated over time and combined with the direct local radiation response. This yielded a final survival field $S_{\mathrm{final}}(\mathbf{x})$, which was then converted to an effective-dose-like map for endpoint extraction. The downstream comparison therefore asked whether the same physical lattice plan produced different peak-valley contrast, peri-tumour spill, organ-at-risk burden, and case ranking once non-local signalling and vascular uptake were considered.

The main value of the model is interpretive rather than predictive in a clinical sense. It does not attempt to reproduce full vascular hemodynamics, and the assay-like outputs derived from the model should be read as biological surrogates rather than direct experimental measurements. Its role in the present study was to test whether conventional physical metrics alone were sufficient to characterize lattice-plan quality, or whether additional biology-informed liability became visible after post-processing.
